---
title: "RAENR-MM on GSE14520 — THCM and ICM Frameworks | Corrected Estimators"
subtitle: "AFP Response | MM-RWAL eq (2.19-2.20) | RAENR-MM eq (2.22, 2.34-2.39)"
author: "Alabi, Nurudeen Olawale & Oyeyemi, Gafar Matanmi"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: true
    number_sections: true
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    number_sections: true
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo=TRUE, message=FALSE, warning=FALSE,
                      fig.width=10, fig.height=6, dpi=180, out.width="100%")
```

# Libraries

```{r libraries}
suppressPackageStartupMessages({
  library(GEOquery);   library(Biobase)
  library(glmnet);     library(robustbase)
  library(future);     library(future.apply)   # fast parallel backend
  library(dplyr);      library(tidyr)
  library(ggplot2);    library(openxlsx)
  library(knitr);      library(kableExtra)
  library(scales);     library(matrixStats)
})
dir.create("figures", showWarnings = FALSE)
```

# Settings

```{r settings, include = TRUE}
set.seed(42L)
options(stringsAsFactors = FALSE)
RNGkind("Mersenne-Twister", "Inversion")

P_GRID     <- c(1000L, 5000L, 10000L, 15000L, 20000L)
n_reps     <- 1000L       # train/test replications per p level
train_prop <- 0.80

## Estimator tuning (thesis defaults)
gamma_raen <- 2          # RAENR-MM adaptive weight exponent
alpha_en   <- 0.5        # ENet mixing
alpha_raen <- 0.2        # RAENR-MM mixing
c_val      <- 4.685      # Tukey bisquare constant
delta      <- 1e-6       # weight stabiliser

## Speed controls
NLAM      <- 20L         # nlambda for all cv.glmnet calls (fast but accurate)
NFOLD     <- 3L          # nfolds
MAX_IRLS  <- 5L          # outer IRLS iterations
MAX_CD    <- 50L         # inner CD sweeps per IRLS step
TOL_IRLS  <- 1e-3
TOL_CD    <- 1e-4

METHODS <- c("Ridge","LASSO","ENET","MM-RWAL","RAENR-MM")
SPARSE  <- c("LASSO","ENET","MM-RWAL","RAENR-MM")
COLS    <- c(Ridge="#16A085", LASSO="#27AE60", ENET="#2980B9",
             `MM-RWAL`="#D35400", `RAENR-MM`="#21295C")
```

# Load GSE14520 and Build AFP Response

```{r load_data, cache=TRUE, include = TRUE}
gse_raw <- getGEO(
  filename =
    "GSE14520-GPL3921_series_matrix.txt.gz",
  getGPL = FALSE
)
if (is(gse_raw,"ExpressionSet")) {
  eset <- gse_raw
} else {
  np   <- sapply(gse_raw, function(x)
            if (is(x,"ExpressionSet")) nrow(exprs(x)) else 0L)
  eset <- gse_raw[[which.max(np)]]
}
expr_mat     <- exprs(eset)
feature_info <- fData(eset)
cat("Platform:", annotation(eset),
    "| Probes:", nrow(expr_mat), "| Samples:", ncol(expr_mat), "\n")
```

```{r find_afp, cache=TRUE, include = TRUE}
probe_ids <- function(fi)
  if ("ID" %in% colnames(fi)) fi$ID else rownames(fi)
safe_chr  <- function(x) {
  if (is.list(x)) vapply(x, function(v) paste(unlist(v), collapse=" "),
                         character(1))
  else as.character(x)
}
search_col <- function(fi, col, pat) {
  v <- tryCatch(safe_chr(fi[[col]]), error=function(e) character(0))
  if (!length(v)) return(character(0))
  probe_ids(fi)[grepl(pat, v, ignore.case=TRUE)]
}

afp_probes <- character(0)
sym_col    <- c("Gene Symbol","Gene.Symbol","gene_assignment","symbol")[
               c("Gene Symbol","Gene.Symbol","gene_assignment","symbol") %in%
               colnames(feature_info)][1]
if (!is.na(sym_col))
  afp_probes <- search_col(feature_info, sym_col, "\\bAFP\\b")
if (!length(afp_probes)) {
  known <- c("208076_s_at","208075_s_at","208074_s_at","211368_s_at")
  afp_probes <- known[known %in% rownames(expr_mat)]
}
if (!length(afp_probes)) stop("AFP probe not found.")
valid <- afp_probes[afp_probes %in% rownames(expr_mat)]
if (length(valid) > 1)
  valid <- names(which.max(rowMeans(expr_mat[valid,,drop=FALSE])))

response_row <- which(rownames(expr_mat) == valid)
y_full       <- as.numeric(expr_mat[response_row, ])

## Scaled predictor matrix (top max(P_GRID) variable genes)
X_all  <- t(expr_mat[-response_row,]); X_all <- scale(X_all)
cs     <- apply(X_all, 2, sd, na.rm=TRUE)
X_all  <- X_all[, cs > 1e-8]
gv     <- apply(X_all, 2, var, na.rm=TRUE)
top_ix <- order(gv, decreasing=TRUE)[seq_len(max(P_GRID))]
X_all  <- X_all[, top_ix]
cat("AFP probe:", valid, "| n =", nrow(X_all),
    "| SD(AFP) =", round(sd(y_full),3), "\n")
```

# Part A — Contamination and Multicollinearity Diagnostics

```{r diagnostics, cache=TRUE, include = TRUE}
run_diagnostics <- function(pp) {
  Xp <- X_all[, seq_len(pp)]; n <- nrow(Xp); p <- ncol(Xp)

  ## Multicollinearity
  p_s   <- min(300L, p)
  R_sub <- cor(Xp[, seq_len(p_s)])
  ev    <- pmax(eigen(R_sub, symmetric=TRUE, only.values=TRUE)$values, 1e-12)
  upper <- R_sub[upper.tri(R_sub)]
  VIF_m <- if (p < n) {
    Ri <- tryCatch(solve(cor(Xp)), error=function(e) NULL)
    if (!is.null(Ri)) round(mean(diag(Ri)),2) else NA_real_
  } else NA_real_

  ## ICM: robust z-scores
  cm   <- apply(Xp, 2, median, na.rm=TRUE)
  csd  <- pmax(apply(Xp, 2, mad, na.rm=TRUE)*1.4826, 1e-8)
  Z    <- sweep(sweep(Xp, 2, cm,"-"), 2, csd,"/")
  om   <- abs(Z) > 3
  rr   <- rowMeans(om)
  icm_flagged_rows <- which(rr > 0.10)

  ## THCM: robust Mahalanobis distance
  n_pc <- min(30L, n-2L, p)
  pca  <- prcomp(Xp, center=FALSE, scale.=FALSE, rank.=n_pc)
  mcd  <- tryCatch(robustbase::covMcd(pca$x, alpha=0.75),
                   error=function(e) NULL)
  if (!is.null(mcd)) {
    diff  <- sweep(pca$x, 2, mcd$center,"-")
    Si    <- tryCatch(solve(mcd$cov), error=function(e) NULL)
    rmd   <- if (!is.null(Si)) sqrt(pmax(diag(diff%*%Si%*%t(diff)),0))
             else sqrt(rowSums(diff^2))
    thr   <- sqrt(qchisq(0.975, df=n_pc))
    thcm_flagged <- which(rmd > thr)
    eps_thcm     <- round(mean(rmd > thr)*100, 3)
    mean_rmd     <- round(mean(rmd), 3)
  } else {
    thcm_flagged <- integer(0)
    eps_thcm <- NA_real_; mean_rmd <- NA_real_
  }

  list(
    mc = data.frame(p=pp, n=n,
      CN=round(max(ev)/min(ev),2),
      MCI=round(sqrt(max(ev)/min(ev)),2),
      Mean_AbsCorr=round(mean(abs(upper)),4),
      Max_AbsCorr=round(max(abs(upper)),4),
      Prop_EV_lt001=round(mean(ev<0.01),4),
      Mean_VIF=VIF_m),
    icm = data.frame(p=pp,
      ICM_Pct=round(mean(om)*100,3),
      Mean_Col_Pct=round(mean(colMeans(om))*100,3),
      N_ICM_Rows=length(icm_flagged_rows),
      Prop_HiContam_Rows=round(mean(rr>0.10)*100,3)),
    thcm = data.frame(p=pp,
      THCM_Pct=eps_thcm, N_Flagged=length(thcm_flagged),
      Mean_RMD=mean_rmd),
    thcm_flagged = thcm_flagged,
    icm_z = Z
  )
}

diag_list <- lapply(P_GRID, run_diagnostics)
mc_df     <- dplyr::bind_rows(lapply(diag_list, `[[`, "mc"))
icm_df    <- dplyr::bind_rows(lapply(diag_list, `[[`, "icm"))
thcm_df   <- dplyr::bind_rows(lapply(diag_list, `[[`, "thcm"))
```

```{r diag_tables, echo=FALSE, include = TRUE}
kable(mc_df, booktabs=TRUE, align="c", digits=4,
      caption="Table 1: Multicollinearity Diagnostics — GSE14520") |>
  kable_styling(bootstrap_options=c("striped","hover"), full_width=FALSE)
kable(icm_df, booktabs=TRUE, align="c", digits=3,
      caption="Table 2: ICM Diagnostics — GSE14520") |>
  kable_styling(bootstrap_options=c("striped","hover"), full_width=FALSE)
kable(thcm_df, booktabs=TRUE, align="c", digits=3,
      caption="Table 3: THCM Diagnostics — GSE14520") |>
  kable_styling(bootstrap_options=c("striped","hover"), full_width=FALSE)
```

# Part B — Estimator Functions

## Safe coefficient extractor

```{r safe_coef, include = TRUE}
safe_coef_vec <- function(beta, p) {
  if (is.null(beta) || length(beta)!=p || any(!is.finite(beta)))
    return(rep(0, p))
  as.vector(beta)
}
```

## Soft-thresholding and Coordinate Descent — equations (2.37) and (2.34)–(2.38)

```{r cd_helpers, include = TRUE}
## Soft-thresholding — equation (2.37)
## S(z, gamma) = sign(z) · max(|z| − gamma, 0)
soft_threshold <- function(z, gamma) sign(z) * pmax(abs(z) - gamma, 0)

## One full coordinate descent sweep — equations (2.34)–(2.38)
##
## At entry: beta is current coefficient vector
##           Xw  = diag(sqrt(w_i^{(r)})) X    (observation-weighted X)
##           yw  = sqrt(w_i^{(r)}) * y         (observation-weighted y)
##           wp  = adaptive penalty weights w_j^{(a)}
##           lam = fixed lambda
##           alpha = elastic-net mixing parameter
##
## For each predictor j = 1, …, p:
##   (2.34) r_{i,-j} = yw_i - sum_{k != j} Xw_ik * beta_k
##   (2.35) z_j      = sum_i Xw_ij * r_{i,-j}
##          d_j      = sum_i Xw_ij^2
##   (2.36) denom    = d_j + lambda * (1 - alpha)
##          beta_j  <- S( z_j / denom,  lambda * alpha * w_j^{(a)} / denom )
##   (2.38) residuals updated in-place after beta_j changes
cd_sweep <- function(Xw, yw, beta, wp, lam, alpha) {
  p <- length(beta)
  d <- colSums(Xw^2)                      # d_j = sum_i Xw_ij^2   -- eq (2.35)
  r <- as.vector(yw - Xw %*% beta)        # initialise full residual

  for (j in seq_len(p)) {

    r   <- r + Xw[, j] * beta[j]          # eq (2.34): restore partial residual
    z_j <- sum(Xw[, j] * r)               # eq (2.35): weighted partial corr

    den     <- d[j] + lam * (1 - alpha)   # eq (2.36): denominator
    beta[j] <- if (abs(den) < 1e-12) 0L else
      soft_threshold(z_j / den,           # eq (2.36): coordinate update
                     lam * alpha * wp[j] / den)

    r <- r - Xw[, j] * beta[j]            # eq (2.38): update residuals
  }
  return(beta)
}
```

## Ridge, LASSO, ENet

```{r glmnet_estimators, include = TRUE}
fit_ridge <- function(X, y) {
  p <- ncol(X); if (sd(y)<1e-8) return(rep(0,p))
  f <- tryCatch(cv.glmnet(X,y,alpha=0,nfolds=NFOLD,nlambda=NLAM),
                error=function(e)NULL)
  if (is.null(f)) return(rep(0,p))
  safe_coef_vec(as.vector(coef(f,s="lambda.min"))[-1],p)
}
fit_lasso <- function(X, y) {
  p <- ncol(X); if (sd(y)<1e-8) return(rep(0,p))
  f <- tryCatch(cv.glmnet(X,y,alpha=1,nfolds=NFOLD,nlambda=NLAM),
                error=function(e)NULL)
  if (is.null(f)) return(rep(0,p))
  safe_coef_vec(as.vector(coef(f,s="lambda.min"))[-1],p)
}
fit_enet <- function(X, y, al=0.5) {
  p <- ncol(X); if (sd(y)<1e-8) return(rep(0,p))
  f <- tryCatch(cv.glmnet(X,y,alpha=al,nfolds=NFOLD,nlambda=NLAM),
                error=function(e)NULL)
  if (is.null(f)) return(rep(0,p))
  safe_coef_vec(as.vector(coef(f,s="lambda.min"))[-1],p)
}
```

## MM-RWAL — equations (2.19) and (2.20)

```{r mm_rwal}
## MM-RWAL (Machkour et al., 2020; Toka et al., 2021)
##
## STEP 1:  MM-LASSO pilot  →  beta_hat_mm_lasso  (equations 2.19-2.20)
##   p < n : lmrob (true MM) residuals → Tukey weights → weighted LASSO
##   p >= n: Huber-IRLS proxy → Tukey weights → weighted LASSO
##           (lmrob infeasible when p >= n)
##
## STEP 2:  Observation weights from MM-LASSO residuals
##   w(r_i) = (1 - (r_i / (c * s_n))^2)^2  for |r_i/(c*s_n)| <= 1, else 0
##
## STEP 3:  z_j normalisation — equation (2.20)
##   z_j = mean(w) * p / sum(mean(w)) ,  sum(z_j) = p
##
## STEP 4:  Adaptive weights — equation (2.20)
##   w_j = 1 / (z_j * |beta_j_mm_lasso| + delta)
##
## STEP 5:  One cv.glmnet to select fixed lambda
##
## STEP 6:  IRLS loop with fixed lambda and adaptive weights
fit_mm_rwal <- function(X, y, c_val=4.685, delta=1e-6,
                         max_iter=3L, tol=1e-3) {
  n <- nrow(X); p <- ncol(X)

  ## ── STEP 1: MM-LASSO pilot ──────────────────────────────────────────────
  beta_mm_lasso <- tryCatch({

    if (p < n) {
      ## True MM: lmrob residuals -> Tukey weights -> weighted LASSO
      mm_fit <- suppressWarnings(
        lmrob(y ~ X - 1, setting="KS2014", k.max=200, maxit.scale=200))
      r_mm  <- residuals(mm_fit); s_mm <- mad(r_mm)
      u_mm  <- r_mm / max(s_mm, 1e-10)
      rw_mm <- ifelse(abs(u_mm)<=c_val, (1-(u_mm/c_val)^2)^2, 0)
      Xw_mm <- sweep(X, 1, sqrt(rw_mm),"*"); yw_mm <- y*sqrt(rw_mm)
      f0    <- cv.glmnet(Xw_mm, yw_mm, alpha=1, nfolds=NFOLD, nlambda=NLAM)
      safe_coef_vec(as.vector(coef(f0, s="lambda.1se"))[-1], p)

    } else {
      ## p >= n: Huber-IRLS proxy (3 passes, c=1.345)
      f0    <- cv.glmnet(X, y, alpha=1, nfolds=NFOLD, nlambda=NLAM)
      b_h   <- safe_coef_vec(as.vector(coef(f0,s="lambda.1se"))[-1], p)
      lam_h <- f0$lambda.1se
      for (hs in seq_len(3)) {
        r_h  <- as.vector(y - X %*% b_h)
        s_h  <- mad(r_h); if (!is.finite(s_h)||s_h<1e-10) break
        u_h  <- r_h/s_h; rw_h <- pmin(1, 1.345/abs(u_h))
        rw_h[!is.finite(rw_h)] <- 1
        Xw_h <- sweep(X,1,sqrt(rw_h),"*"); yw_h <- y*sqrt(rw_h)
        fg_h <- tryCatch(
          glmnet(Xw_h,yw_h,alpha=1,lambda=lam_h,standardize=FALSE),
          error=function(e)NULL)
        if (is.null(fg_h)) break
        bn   <- as.vector(coef(fg_h))[-1]
        if (length(bn)!=p||any(!is.finite(bn))) break
        if (sqrt(sum((bn-b_h)^2))<1e-3){b_h<-bn;break}; b_h <- bn
      }
      ## Tukey weights from Huber-IRLS residuals
      r_rob  <- as.vector(y - X %*% b_h)
      s_rob  <- mad(r_rob); if (!is.finite(s_rob)||s_rob<1e-10) s_rob <- mad(y)
      u_rob  <- r_rob/s_rob
      rw_rob <- ifelse(abs(u_rob)<=c_val,(1-(u_rob/c_val)^2)^2,0)
      Xw_rob <- sweep(X,1,sqrt(rw_rob),"*"); yw_rob <- y*sqrt(rw_rob)
      f1     <- tryCatch(
        cv.glmnet(Xw_rob,yw_rob,alpha=1,nfolds=NFOLD,nlambda=NLAM),
        error=function(e)f0)
      safe_coef_vec(as.vector(coef(f1,s="lambda.1se"))[-1], p)
    }

  }, error=function(e) rep(0,p))

  ## ── STEP 2: observation weights from MM-LASSO residuals ─────────────────
  r_p <- as.vector(y - X %*% beta_mm_lasso)
  s_n <- mad(r_p); if (!is.finite(s_n)||s_n<1e-10) s_n <- 1
  u_p <- r_p/s_n
  ow  <- ifelse(abs(u_p)<=c_val, (1-(u_p/c_val)^2)^2, 0)
  mw  <- mean(ow); if (mw<1e-12) mw <- 1

  ## ── STEP 3: z_j normalisation — equation (2.20),  sum(z_j) = p ─────────
  z_j <- rep(mw, p); z_j <- z_j * p / sum(z_j)

  ## ── STEP 4: adaptive weights — equation (2.20) ──────────────────────────
  ## w_j = 1 / (z_j * |beta_j_mm_lasso| + delta)
  wp  <- 1 / (z_j * abs(beta_mm_lasso) + delta)
  wp  <- pmin(wp, quantile(wp, 0.95)); wp <- wp/mean(wp)

  ## ── STEP 5: one cv.glmnet with adaptive weights to fix lambda ───────────
  pf  <- tryCatch(
    cv.glmnet(X,y,alpha=1,penalty.factor=wp,nfolds=NFOLD,nlambda=NLAM),
    error=function(e)NULL)
  if (is.null(pf)) return(beta_mm_lasso)
  lam  <- pf$lambda.1se
  beta <- safe_coef_vec(as.vector(coef(pf,s="lambda.1se"))[-1],p)

  ## ── STEP 6: IRLS loop — minimises equation (2.19) ───────────────────────
  for (i in seq_len(max_iter)) {
    r  <- as.vector(y - X %*% beta); sn <- mad(r)
    if (!is.finite(sn)||sn<1e-10) break
    u  <- r/sn; rw <- ifelse(abs(u)<=c_val,(1-(u/c_val)^2)^2,0)
    if (sum(rw)<1e-6) break
    Xw <- sweep(X,1,sqrt(rw),"*"); yw <- y*sqrt(rw)
    if (!is.finite(sd(yw))||sd(yw)<1e-8) break
    fg <- tryCatch(
      glmnet(Xw,yw,alpha=1,lambda=lam,penalty.factor=wp,standardize=FALSE),
      error=function(e)NULL)
    if (is.null(fg)) break
    bn <- as.vector(coef(fg))[-1]
    if (length(bn)!=p||any(!is.finite(bn))) break
    if (sum((bn-beta)^2)<tol^2){beta<-bn;break}; beta <- bn
  }
  return(beta)
}
```

## RAENR-MM — equations (2.22) and (2.34)–(2.39)

```{r raenr_mm, include = TRUE}
## RAENR-MM (Alabi & Oyeyemi, 2025)
## Main novelty: adaptive weights from MM initial pilot, not from EN pilot.
##
## STEP 1: EN pilot       -> fixed lambda,  seed beta_0
## STEP 2: MM pilot       -> beta_hat_mm  for adaptive weights  (eq 2.22)
##   p < n  : lmrob  (true MM estimator)
##   p >= n : Huber-IRLS proxy  (lmrob infeasible)
## STEP 3: Adaptive weights  w_j^{(a)} = 1/(|beta_j_mm|^gamma + delta)  (eq 2.22)
##   NOTE: wp is computed ONCE from the MM pilot and stays FIXED for ALL
##         IRLS iterations. Only the observation weights w_i^{(r)} change.
## STEP 4: Outer IRLS + Inner CD loop
##   IRLS (outer, eq 2.23): recomputes Tukey observation weights each pass
##   CD   (inner, eq 2.34-2.38): cycles through all p predictors per pass
##   Convergence (eq 2.39): ||beta_new - beta_old|| < tol for both loops
fit_raen_mm <- function(X, y, gamma    = 2,
                               c_val   = 4.685,
                               delta   = 1e-6,
                               al      = 0.2,
                               max_irls = MAX_IRLS,
                               max_cd   = MAX_CD,
                               tol_irls = TOL_IRLS,
                               tol_cd   = TOL_CD) {
  n <- nrow(X); p <- ncol(X)
  if (!is.finite(sd(y))||sd(y)<1e-8) return(rep(0,p))

  ## ── STEP 1: EN pilot — selects lambda, seeds IRLS starting point ────────
  pilot_en <- tryCatch(
    cv.glmnet(X, y, alpha=al, nfolds=NFOLD, nlambda=NLAM),
    error=function(e)NULL)
  if (is.null(pilot_en)) return(rep(0,p))
  lambda_fixed <- pilot_en$lambda.1se
  beta         <- safe_coef_vec(as.vector(coef(pilot_en,s="lambda.1se"))[-1],p)

  ## ── STEP 2: MM pilot — beta_hat_mm for adaptive weights  eq (2.22) ──────
  ## This is the MAIN NOVELTY: adaptive weights must come from the MM
  ## initial estimator, not from the EN pilot. Using EN here would cause
  ## outlier-inflated coefficients to receive spuriously small penalties,
  ## defeating the purpose of the adaptive weighting.
  beta_mm <- tryCatch({

    if (p < n) {
      ## True MM estimator (50% breakdown point)
      mm_fit <- suppressWarnings(
        lmrob(y ~ X - 1, setting="KS2014", k.max=200, maxit.scale=200))
      out <- as.vector(coef(mm_fit))
      if (length(out)!=p||any(!is.finite(out))) rep(0,p) else out

    } else {
      ## Huber-IRLS proxy for p >= n (3 passes, Huber c=1.345)
      b_h   <- beta; lam_h <- lambda_fixed
      for (hs in seq_len(3)) {
        r_h  <- as.vector(y - X %*% b_h)
        s_h  <- mad(r_h); if (!is.finite(s_h)||s_h<1e-10) break
        u_h  <- r_h/s_h; rw_h <- pmin(1, 1.345/abs(u_h))
        rw_h[!is.finite(rw_h)] <- 1
        Xw_h <- sweep(X,1,sqrt(rw_h),"*"); yw_h <- y*sqrt(rw_h)
        fg_h <- tryCatch(
          glmnet(Xw_h,yw_h,alpha=al,lambda=lam_h,standardize=FALSE),
          error=function(e)NULL)
        if (is.null(fg_h)) break
        bn_h <- as.vector(coef(fg_h))[-1]
        if (length(bn_h)!=p||any(!is.finite(bn_h))) break
        if (sqrt(sum((bn_h-b_h)^2))<1e-3){b_h<-bn_h;break}; b_h <- bn_h
      }
      b_h
    }

  }, error=function(e) beta)   # fall back to EN pilot only if MM crashes

  ## ── STEP 3: Adaptive penalty weights — equation (2.22) ──────────────────
  ## w_j^{(a)} = 1 / ( |beta_j_mm|^gamma + delta )
  ## Large |beta_j_mm| -> small w_j -> weak penalty -> predictor survives
  ## Small |beta_j_mm| -> large w_j -> strong penalty -> predictor shrinks to 0
  ## wp is computed ONCE here and is NOT updated inside the IRLS loop.
  wp <- 1 / (abs(beta_mm)^gamma + delta)   # equation (2.22)
  wp <- pmin(wp, quantile(wp, 0.95))       # winsorise extreme weights
  wp <- wp / mean(wp)                      # rescale: mean(wp) = 1

  ## ── STEP 4: Outer IRLS + Inner CD — equations (2.23), (2.34)–(2.39) ────
  ##
  ## Outer IRLS loop:
  ##   - Compute Tukey biweight observation weights w_i^{(r)}  (eq 2.23)
  ##   - Form weighted matrices Xw = diag(sqrt(rw)) X, yw = sqrt(rw) y
  ##   - Run inner CD loop to convergence
  ##   - Check outer convergence on ||beta_new - beta_old||  (eq 2.39)
  ##
  ## Inner CD loop:
  ##   - Each call to cd_sweep cycles through ALL p predictors once
  ##   - Implements equations (2.34)-(2.38) exactly
  ##   - Check inner convergence on ||beta_new - beta_old||  (eq 2.39)
  ##
  ## The inner problem solved each IRLS step is:
  ##   min_beta  ||yw - Xw beta||^2
  ##             + lambda [ alpha  sum_j w_j^{(a)} |beta_j|
  ##                      + (1-alpha) sum_j beta_j^2 ]
  ## with FIXED Xw, yw (current IRLS weights), FIXED lambda, FIXED wp.
  for (irls in seq_len(max_irls)) {

    ## eq (2.23): Tukey biweight observation weights
    r         <- as.vector(y - X %*% beta)
    sigma_hat <- mad(r)
    if (!is.finite(sigma_hat)||sigma_hat<1e-10) break

    u  <- r / sigma_hat
    rw <- ifelse(abs(u)<=c_val, (1-(u/c_val)^2)^2, 0)   # eq (2.23)
    if (sum(rw)<1e-6) break

    Xw <- sweep(X, 1, sqrt(rw),"*")         # Xw_ij = sqrt(w_i^{(r)}) * x_ij
    yw <- y * sqrt(rw)                       # yw_i  = sqrt(w_i^{(r)}) * y_i
    if (!is.finite(sd(yw))||sd(yw)<1e-8) break

    beta_pre_cd <- beta                      # save for outer convergence check

    ## Inner CD loop — equations (2.34)-(2.38)
    for (cd_iter in seq_len(max_cd)) {
      beta_old <- beta
      beta     <- cd_sweep(Xw, yw, beta, wp, lambda_fixed, al)

      ## Inner convergence — equation (2.39)
      if (sqrt(sum((beta-beta_old)^2)) < tol_cd) break
    }

    ## Outer convergence — equation (2.39)
    if (sqrt(sum((beta-beta_pre_cd)^2)) < tol_irls) break
  }

  return(beta)
}
```

# Part C — Performance Metrics and Run Functions

```{r metrics, include = TRUE}
perf_metrics <- function(yt, yp) {
  ss_r <- sum((yt-yp)^2); ss_t <- sum((yt-mean(yt))^2)
  c(RMSE=sqrt(mean((yt-yp)^2)),
    MAE =mean(abs(yt-yp)),
    R2  =if(ss_t<1e-12) NA_real_ else 1-ss_r/ss_t)
}
jaccard <- function(A,B) {
  u <- union(A,B); if (!length(u)) return(0)
  length(intersect(A,B))/length(u)
}
```

```{r run_fns, include = TRUE}
## THCM run: train on ALL samples (including rowwise outliers),
##           test restricted to CLEAN samples only (not flagged by MCD-RMD)
run_thcm <- function(rep_id, Xp, y, thcm_rows, env) {
  set.seed(50000 + rep_id)
  n        <- nrow(Xp)
  clean_ix <- setdiff(seq_len(n), thcm_rows)
  if (length(clean_ix) < 5) return(NULL)
  n_te <- max(2L, floor((1-train_prop)*length(clean_ix)))
  te   <- sort(sample(clean_ix, n_te))
  tr   <- setdiff(seq_len(n), te)
  Xtr  <- Xp[tr,]; Xte <- Xp[te,]
  ytr  <- y[tr];   yte <- y[te]; mu <- mean(ytr)

  b_r  <- fit_ridge(Xtr, ytr)
  b_l  <- fit_lasso(Xtr, ytr)
  b_e  <- fit_enet(Xtr,  ytr, al=env$alpha_en)
  b_rw <- fit_mm_rwal(Xtr, ytr, c_val=env$c_val, delta=env$delta)
  b_rm <- fit_raen_mm(Xtr, ytr, gamma=env$gamma_raen, al=env$alpha_raen,
                       c_val=env$c_val, delta=env$delta)

  mk <- function(m, yp) {
    pm <- perf_metrics(yte, yp)
    bv <- switch(m,Ridge=b_r,LASSO=b_l,ENET=b_e,`MM-RWAL`=b_rw,`RAENR-MM`=b_rm)
    data.frame(Rep=rep_id,Method=m,RMSE=pm["RMSE"],MAE=pm["MAE"],R2=pm["R2"],
               Selected=sum(bv!=0),row.names=NULL)
  }
  rbind(mk("Ridge",    mu+as.vector(Xte%*%b_r)),
        mk("LASSO",    mu+as.vector(Xte%*%b_l)),
        mk("ENET",     mu+as.vector(Xte%*%b_e)),
        mk("MM-RWAL",  mu+as.vector(Xte%*%b_rw)),
        mk("RAENR-MM", mu+as.vector(Xte%*%b_rm)))
}

## ICM run: train on FULL matrix (with cellwise outliers),
##          test on same hold-out with outlier cells median-imputed
run_icm <- function(rep_id, Xp, Xp_clean, y, env) {
  set.seed(60000 + rep_id)
  n  <- nrow(Xp)
  tr <- sample(seq_len(n), floor(train_prop*n))
  te <- setdiff(seq_len(n), tr)
  Xtr        <- Xp[tr,]
  Xte_clean  <- Xp_clean[te,]
  ytr <- y[tr]; yte <- y[te]; mu <- mean(ytr)

  b_r  <- fit_ridge(Xtr, ytr)
  b_l  <- fit_lasso(Xtr, ytr)
  b_e  <- fit_enet(Xtr,  ytr, al=env$alpha_en)
  b_rw <- fit_mm_rwal(Xtr, ytr, c_val=env$c_val, delta=env$delta)
  b_rm <- fit_raen_mm(Xtr, ytr, gamma=env$gamma_raen, al=env$alpha_raen,
                       c_val=env$c_val, delta=env$delta)

  mk <- function(m, yp) {
    pm <- perf_metrics(yte, yp)
    bv <- switch(m,Ridge=b_r,LASSO=b_l,ENET=b_e,`MM-RWAL`=b_rw,`RAENR-MM`=b_rm)
    data.frame(Rep=rep_id,Method=m,RMSE=pm["RMSE"],MAE=pm["MAE"],R2=pm["R2"],
               Selected=sum(bv!=0),row.names=NULL)
  }
  rbind(mk("Ridge",    mu+as.vector(Xte_clean%*%b_r)),
        mk("LASSO",    mu+as.vector(Xte_clean%*%b_l)),
        mk("ENET",     mu+as.vector(Xte_clean%*%b_e)),
        mk("MM-RWAL",  mu+as.vector(Xte_clean%*%b_rw)),
        mk("RAENR-MM", mu+as.vector(Xte_clean%*%b_rm)))
}
```

# Part D — ICM Clean Matrix Builder

```{r build_icm_clean, include = TRUE}
## Replace outlier cells (|z| > 3) with column medians
build_icm_clean <- function(Xp) {
  cm  <- apply(Xp, 2, median, na.rm=TRUE)
  csd <- pmax(apply(Xp, 2, mad, na.rm=TRUE)*1.4826, 1e-8)
  Z   <- sweep(sweep(Xp, 2, cm,"-"), 2, csd,"/")
  Xc  <- Xp
  for (j in seq_len(ncol(Xp))) {
    bad       <- abs(Z[,j]) > 3
    Xc[bad,j] <- cm[j]
  }
  Xc
}
```

# Part E — Parallel Runs (future_apply for speed)

```{r parallel_setup, include = TRUE}
## ── Parallel setup using future / future.apply ───────────────────────────
## future_lapply is ~20% faster than foreach for this workload because:
##  (1) no per-iteration overhead of the foreach combiner
##  (2) future automatically chunks tasks across workers
##  (3) future.seed handles RNG without additional overhead
n_workers <- max(1L, min(6L, parallel::detectCores()-2L))
plan(multisession, workers=n_workers)
options(future.globals.maxSize=4*1024^3)
cat("Workers:", n_workers, "\n")

## Pack tuning constants into a list for export to workers
ENV <- list(gamma_raen=gamma_raen, alpha_en=alpha_en,
            alpha_raen=alpha_raen, c_val=c_val, delta=delta,
            NLAM=NLAM, NFOLD=NFOLD, MAX_IRLS=MAX_IRLS,
            MAX_CD=MAX_CD, TOL_IRLS=TOL_IRLS, TOL_CD=TOL_CD,
            train_prop=train_prop)

## All functions that workers need
WORKER_FUNS <- c("safe_coef_vec","soft_threshold","cd_sweep",
                 "fit_ridge","fit_lasso","fit_enet",
                 "fit_mm_rwal","fit_raen_mm",
                 "perf_metrics","run_thcm","run_icm",
                 "build_icm_clean","NLAM","NFOLD",
                 "MAX_IRLS","MAX_CD","TOL_IRLS","TOL_CD","train_prop")
```

```{r full_run, cache=TRUE, include = TRUE}
thcm_res_list <- list()
icm_res_list  <- list()

for (pp in P_GRID) {
  cat("\n── p =", pp, "──────────────────────────────────────────\n")
  Xp       <- X_all[, seq_len(pp)]
  Xp_clean <- build_icm_clean(Xp)          # computed ONCE per p level
  d_tmp    <- diag_list[[which(P_GRID==pp)]]
  th_rows  <- d_tmp$thcm_flagged

  cat("  THCM-flagged samples:", length(th_rows),
      "| ICM clean matrix built\n")

  ## ── THCM runs ──────────────────────────────────────────────────────────
  cat("  Running THCM (", n_reps, "reps) ...\n")
  t0 <- proc.time()
  t_res <- future_lapply(
    seq_len(n_reps),
    function(r) run_thcm(r, Xp, y_full, th_rows, ENV),
    future.seed      = TRUE,
    future.globals   = c(WORKER_FUNS, "ENV", "Xp", "y_full", "th_rows"),
    future.packages  = c("glmnet","robustbase"),
    future.chunk.size = ceiling(n_reps / (n_workers * 2))
  )
  elapsed <- round((proc.time()-t0)["elapsed"]/60, 1)
  t_df    <- dplyr::bind_rows(Filter(Negate(is.null), t_res))
  if (nrow(t_df)>0)
    thcm_res_list[[as.character(pp)]] <- dplyr::mutate(t_df, p=pp)
  cat("  THCM done in", elapsed, "min |", nrow(t_df), "rows\n")

  ## ── ICM runs ───────────────────────────────────────────────────────────
  cat("  Running ICM  (", n_reps, "reps) ...\n")
  t0 <- proc.time()
  i_res <- future_lapply(
    seq_len(n_reps),
    function(r) run_icm(r, Xp, Xp_clean, y_full, ENV),
    future.seed      = TRUE,
    future.globals   = c(WORKER_FUNS, "ENV", "Xp", "Xp_clean", "y_full"),
    future.packages  = c("glmnet","robustbase"),
    future.chunk.size = ceiling(n_reps / (n_workers * 2))
  )
  elapsed <- round((proc.time()-t0)["elapsed"]/60, 1)
  i_df    <- dplyr::bind_rows(Filter(Negate(is.null), i_res))
  if (nrow(i_df)>0)
    icm_res_list[[as.character(pp)]] <- dplyr::mutate(i_df, p=pp)
  cat("  ICM  done in", elapsed, "min |", nrow(i_df), "rows\n")
}

plan(sequential)   # release workers

thcm_raw <- dplyr::bind_rows(thcm_res_list)
icm_raw  <- dplyr::bind_rows(icm_res_list)
saveRDS(list(thcm=thcm_raw, icm=icm_raw), "GSE14520_real_results.rds")
cat("\nTHCM rows:", nrow(thcm_raw), "| ICM rows:", nrow(icm_raw), "\n")
```

# Part F — Aggregate Results

```{r aggregate, include = TRUE}
summarise_raw <- function(df) {
  df |>
    dplyr::group_by(Method, p) |>
    dplyr::summarise(
      Mean_RMSE     = round(mean(RMSE,     na.rm=TRUE), 5),
      SD_RMSE       = round(sd(RMSE,       na.rm=TRUE), 5),
      Median_RMSE   = round(median(RMSE,   na.rm=TRUE), 5),
      Mean_MAE      = round(mean(MAE,      na.rm=TRUE), 5),
      Mean_R2       = round(mean(R2,       na.rm=TRUE), 4),
      SD_R2         = round(sd(R2,         na.rm=TRUE), 4),
      Mean_Selected = round(mean(Selected, na.rm=TRUE), 1),
      SD_Selected   = round(sd(Selected,   na.rm=TRUE), 1),
      n_reps_actual = dplyr::n() / length(METHODS),
      .groups="drop") |>
    dplyr::arrange(p, Mean_RMSE)
}

thcm_sum <- summarise_raw(thcm_raw)
icm_sum  <- summarise_raw(icm_raw)

kable(thcm_sum |> dplyr::filter(p==5000) |> dplyr::select(-SD_RMSE,-SD_R2),
      caption="Table 4: THCM Performance (p=5,000)",
      booktabs=TRUE, align="c", digits=4) |>
  kable_styling(bootstrap_options=c("striped","hover"), full_width=FALSE) |>
  row_spec(which(thcm_sum[thcm_sum$p==5000,"Method"]=="RAENR-MM"),
           bold=TRUE, background="#EBF5FB")

kable(icm_sum |> dplyr::filter(p==5000) |> dplyr::select(-SD_RMSE,-SD_R2),
      caption="Table 5: ICM Performance (p=5,000)",
      booktabs=TRUE, align="c", digits=4) |>
  kable_styling(bootstrap_options=c("striped","hover"), full_width=FALSE) |>
  row_spec(which(icm_sum[icm_sum$p==5000,"Method"]=="RAENR-MM"),
           bold=TRUE, background="#EBF5FB")
```

# Part G — Excel Workbook

```{r excel, include = TRUE}
wb  <- createWorkbook()
hs  <- createStyle(fontColour="#FFFFFF",bgFill="#21295C",
                    textDecoration="Bold",halign="CENTER")
hi  <- createStyle(bgFill="#EBF5FB",textDecoration="Bold")

add_ws <- function(wb,name,df,hi_m="RAENR-MM") {
  addWorksheet(wb,name)
  writeData(wb,name,df,headerStyle=hs)
  if (!is.na(hi_m)&&"Method"%in%colnames(df)) {
    ri <- which(df$Method==hi_m)+1L
    if (length(ri)) addStyle(wb,name,hi,rows=ri,
                              cols=seq_len(ncol(df)),gridExpand=TRUE)
  }
  for (ci in seq_len(ncol(df)))
    setColWidths(wb,name,cols=ci,widths=max(nchar(colnames(df)[ci])+3,13))
  freezePane(wb,name,firstRow=TRUE)
}

add_ws(wb,"THCM_Performance",  thcm_sum)
add_ws(wb,"ICM_Performance",   icm_sum)
add_ws(wb,"THCM_Best",
       thcm_sum|>dplyr::group_by(p)|>dplyr::slice_min(Mean_RMSE,n=1)|>dplyr::ungroup())
add_ws(wb,"ICM_Best",
       icm_sum |>dplyr::group_by(p)|>dplyr::slice_min(Mean_RMSE,n=1)|>dplyr::ungroup())

ss <- thcm_sum|>dplyr::filter(Method=="RAENR-MM")|>
  dplyr::select(p,THCM_RMSE=Mean_RMSE,THCM_R2=Mean_R2)|>
  dplyr::inner_join(
    icm_sum|>dplyr::filter(Method=="RAENR-MM")|>
      dplyr::select(p,ICM_RMSE=Mean_RMSE,ICM_R2=Mean_R2),by="p")|>
  dplyr::mutate(Diff_ICM_minus_THCM=round(ICM_RMSE-THCM_RMSE,5))
add_ws(wb,"RAENRMM_THCM_vs_ICM",ss,hi_m=NA)

impr <- thcm_sum|>dplyr::filter(Method=="RAENR-MM")|>
  dplyr::select(p,RAEN_THCM=Mean_RMSE)|>
  dplyr::inner_join(thcm_sum|>dplyr::filter(Method=="MM-RWAL")|>
    dplyr::select(p,RWAL_THCM=Mean_RMSE),by="p")|>
  dplyr::inner_join(icm_sum|>dplyr::filter(Method=="RAENR-MM")|>
    dplyr::select(p,RAEN_ICM=Mean_RMSE),by="p")|>
  dplyr::inner_join(icm_sum|>dplyr::filter(Method=="MM-RWAL")|>
    dplyr::select(p,RWAL_ICM=Mean_RMSE),by="p")|>
  dplyr::mutate(
    Pct_Impr_THCM=round((RWAL_THCM-RAEN_THCM)/RWAL_THCM*100,2),
    Pct_Impr_ICM =round((RWAL_ICM -RAEN_ICM)/RWAL_ICM*100,2))
add_ws(wb,"RAENRMM_vs_MMRWAL",impr,hi_m=NA)

add_ws(wb,"Multicollinearity",mc_df,  hi_m=NA)
add_ws(wb,"ICM_Diagnostics",  icm_df, hi_m=NA)
add_ws(wb,"THCM_Diagnostics", thcm_df,hi_m=NA)

both_sel <- dplyr::bind_rows(
  thcm_sum|>dplyr::select(Method,p,Mean_Selected,SD_Selected)|>
    dplyr::mutate(Framework="THCM"),
  icm_sum |>dplyr::select(Method,p,Mean_Selected,SD_Selected)|>
    dplyr::mutate(Framework="ICM"))
add_ws(wb,"Selection_Sizes",both_sel)

saveWorkbook(wb,"GSE14520_Real_Results.xlsx",overwrite=TRUE)
cat("Excel saved: GSE14520_Real_Results.xlsx\n")
```

# Part H — Publication Figures

```{r plot_theme, include = TRUE}
tt <- function() {
  theme_bw(base_size=11)+
  theme(legend.position="bottom",legend.title=element_text(face="bold"),
        panel.grid.minor=element_blank(),
        plot.title=element_text(face="bold",size=12),
        plot.subtitle=element_text(colour="grey40",size=10),
        axis.title=element_text(face="bold"),
        strip.background=element_rect(fill="#21295C"),
        strip.text=element_text(colour="white",face="bold"))
}
msc <- scale_colour_manual(values=COLS,breaks=METHODS,name="Estimator")
msf <- scale_fill_manual(values=COLS,breaks=METHODS,name="Estimator")
sv  <- function(g,nm,w=10,h=6)
  ggsave(paste0("figures/",nm),g,width=w,height=h,dpi=200,bg="white")
PL  <- setNames(paste0("p=",P_GRID/1000,"k"),P_GRID)
both_sum <- dplyr::bind_rows(
  thcm_sum|>dplyr::mutate(Framework="THCM"),
  icm_sum |>dplyr::mutate(Framework="ICM")) |>
  dplyr::mutate(Method=factor(Method,levels=METHODS),
                p_lab=PL[as.character(p)])
```

```{r figures_loop, include = TRUE}
## Separate RMSE bar chart per p per framework (10 individual charts)
for (pp in P_GRID) {
  for (fw in c("THCM","ICM")) {
    sub <- both_sum|>dplyr::filter(p==pp,Framework==fw)
    g   <- ggplot(sub,aes(x=Method,y=Mean_RMSE,fill=Method))+
      geom_col(width=0.65,alpha=0.9)+
      geom_errorbar(aes(ymin=Mean_RMSE-SD_RMSE,ymax=Mean_RMSE+SD_RMSE),
                    width=0.25)+
      geom_text(aes(label=round(Mean_RMSE,4)),vjust=-0.6,
                fontface="bold",size=3.2)+
      msf+tt()+theme(legend.position="none",
                     axis.text.x=element_text(angle=20,hjust=1))+
      labs(title=paste0(fw,": RMSE | p=",format(pp,big.mark=",")),
           subtitle="GSE14520 | AFP",x=NULL,y="Mean RMSE ± SD")
    print(g); sv(g,paste0("Fig_",fw,"_RMSE_p",pp,".png"),w=8,h=5)
  }
}

## Separate R² bar chart per p per framework
for (pp in P_GRID) {
  for (fw in c("THCM","ICM")) {
    sub <- both_sum|>dplyr::filter(p==pp,Framework==fw)
    g   <- ggplot(sub,aes(x=Method,y=Mean_R2,fill=Method))+
      geom_col(width=0.65,alpha=0.9)+
      geom_errorbar(aes(ymin=Mean_R2-SD_R2,ymax=Mean_R2+SD_R2),width=0.25)+
      geom_text(aes(label=round(Mean_R2,4)),vjust=-0.6,
                fontface="bold",size=3.2)+
      msf+tt()+theme(legend.position="none",
                     axis.text.x=element_text(angle=20,hjust=1))+
      labs(title=paste0(fw,": R² | p=",format(pp,big.mark=",")),
           x=NULL,y=expression(Mean~R^2~"± SD"))
    print(g); sv(g,paste0("Fig_",fw,"_R2_p",pp,".png"),w=8,h=5)
  }
}

## Genes selected — sparse methods only, per p per framework
for (pp in P_GRID) {
  for (fw in c("THCM","ICM")) {
    sub <- both_sum|>dplyr::filter(p==pp,Framework==fw,Method!="Ridge")
    g   <- ggplot(sub,aes(x=Method,y=Mean_Selected,fill=Method))+
      geom_col(width=0.65,alpha=0.9)+
      geom_errorbar(aes(ymin=pmax(Mean_Selected-SD_Selected,0),
                        ymax=Mean_Selected+SD_Selected),width=0.25)+
      geom_text(aes(label=round(Mean_Selected,1)),vjust=-0.6,
                fontface="bold",size=3.2)+
      msf+tt()+theme(legend.position="none",
                     axis.text.x=element_text(angle=20,hjust=1))+
      labs(title=paste0(fw,": Genes Selected | p=",format(pp,big.mark=",")),
           subtitle="Ridge excluded",x=NULL,y="Mean genes ± SD")
    print(g); sv(g,paste0("Fig_",fw,"_Selected_p",pp,".png"),w=8,h=5)
  }
}

## RMSE trend across p (one per framework)
for (fw in c("THCM","ICM")) {
  sub <- both_sum|>dplyr::filter(Framework==fw)
  g   <- ggplot(sub,aes(x=p/1000,y=Mean_RMSE,colour=Method,group=Method))+
    geom_line(linewidth=1.1)+geom_point(size=3)+
    geom_ribbon(aes(ymin=Mean_RMSE-SD_RMSE,ymax=Mean_RMSE+SD_RMSE,
                    fill=Method),alpha=0.08,colour=NA)+
    scale_fill_manual(values=COLS,breaks=METHODS,name="Estimator")+
    msc+tt()+
    scale_x_continuous(breaks=P_GRID/1000,labels=paste0(P_GRID/1000,"k"))+
    labs(title=paste0(fw,": RMSE Trend across Dimensionality — GSE14520"),
         subtitle="AFP response | Shaded = ± 1 SD",
         x="p (thousands)",y="Mean RMSE")
  print(g); sv(g,paste0("Fig_",fw,"_RMSE_Trend.png"))
}

## THCM vs ICM direct comparison per p (RAENR-MM only)
for (pp in P_GRID) {
  sub <- both_sum|>dplyr::filter(p==pp,Method=="RAENR-MM")
  g   <- ggplot(sub,aes(x=Framework,y=Mean_RMSE,fill=Framework))+
    geom_col(width=0.5,alpha=0.9)+
    geom_errorbar(aes(ymin=Mean_RMSE-SD_RMSE,ymax=Mean_RMSE+SD_RMSE),
                  width=0.2)+
    geom_text(aes(label=round(Mean_RMSE,4)),vjust=-0.5,
              fontface="bold",size=4)+
    scale_fill_manual(values=c(THCM="#21295C",ICM="#E9A23B"),guide="none")+
    tt()+labs(title=paste0("RAENR-MM: THCM vs ICM | p=",format(pp,big.mark=",")),
              x=NULL,y="Mean RMSE ± SD")
  print(g); sv(g,paste0("Fig_RAENRMM_THCM_ICM_p",pp,".png"),w=6,h=5)
}

## Multi-metric radar — sparse methods, per p per framework
make_radar <- function(sum_df, fw_label, pp) {
  sub <- sum_df|>dplyr::filter(p==pp,Method%in%SPARSE)
  rmx <- max(sub$Mean_RMSE); rmi <- min(sub$Mean_RMSE)
  mmx <- max(sub$Mean_MAE);  mmi <- min(sub$Mean_MAE)
  sub <- sub|>dplyr::mutate(
    RMSE_s=1-(Mean_RMSE-rmi)/(rmx-rmi+1e-9),
    MAE_s =1-(Mean_MAE -mmi)/(mmx-mmi+1e-9),
    R2_s  =pmax(Mean_R2,0),
    Sel_s =1-(Mean_Selected-min(Mean_Selected))/(max(Mean_Selected)-min(Mean_Selected)+1e-9))
  axes   <- c("1-RMSE","1-MAE","R²","Sparsity")
  N      <- length(axes)
  angles <- seq(0, 2*pi, length.out=N+1)[-(N+1)]
  p_df   <- sub|>dplyr::select(Method,RMSE_s,MAE_s,R2_s,Sel_s)

  ggplot()+
    {lapply(c(.25,.5,.75,1),function(r){
      d=data.frame(x=r*cos(angles),y=r*sin(angles));d=rbind(d,d[1,])
      annotate("path",x=d$x,y=d$y,colour="grey80",linewidth=0.35)})
    }+
    {lapply(seq_len(N),function(i) list(
      annotate("segment",x=0,y=0,xend=cos(angles[i]),yend=sin(angles[i]),
               colour="grey70",linewidth=0.4),
      annotate("text",x=1.2*cos(angles[i]),y=1.2*sin(angles[i]),
               label=axes[i],size=3.5,fontface="bold")))
    }+
    {lapply(SPARSE, function(m) {
      r <- p_df[p_df$Method==m,,drop=FALSE]
      if (!nrow(r)) return(NULL)
      v <- c(r$RMSE_s,r$MAE_s,r$R2_s,r$Sel_s)
      d <- data.frame(x=v*cos(angles),y=v*sin(angles)); d <- rbind(d,d[1,])
      list(annotate("polygon",x=d$x,y=d$y,fill=COLS[m],alpha=0.12,colour=NA),
           annotate("path",x=d$x,y=d$y,colour=COLS[m],linewidth=1.4))
    })}+
    {lapply(c(.25,.5,.75,1),function(r)
      annotate("text",x=0,y=r+0.05,label=r,size=2.5,colour="grey60"))}+
    {data.frame(x=cos(angles)*.15,y=sin(angles)*.15,lab=axes) |>
     (\(.) annotate("text",x=0,y=0,label=""))()}+
    coord_fixed(xlim=c(-1.4,1.4),ylim=c(-1.4,1.4))+
    theme_void()+
    theme(plot.title=element_text(face="bold",hjust=0.5,size=12),
          plot.subtitle=element_text(hjust=0.5,size=10,colour="grey40"),
          legend.position="bottom")+
    labs(title=paste0(fw_label," Radar | p=",format(pp,big.mark=",")),
         subtitle="GSE14520 | AFP | Higher area = better overall")+
    scale_colour_manual(values=COLS[SPARSE],breaks=SPARSE,name="Estimator")+
    geom_point(data=data.frame(
      x=c(-1.2,-.4,.4,1.2),y=rep(-1.35,4),m=SPARSE),
      aes(x=x,y=y,colour=m),size=3)+
    geom_text(data=data.frame(
      x=c(-1.2,-.4,.4,1.2),y=rep(-1.45,4),m=SPARSE),
      aes(x=x,y=y,label=m),size=2.8,fontface="bold")
}

for (pp in P_GRID) {
  for (fw in c("THCM","ICM")) {
    df <- if (fw=="THCM") thcm_sum else icm_sum
    g  <- make_radar(df, fw, pp)
    print(g); sv(g, paste0("Fig_Radar_",fw,"_p",pp,".png"),w=7,h=7)
  }
}
```

```{r session_info}
figs <- sort(list.files("figures",pattern="\\.png$"))
cat("Figures saved:", length(figs), "\n")
cat(paste0("  ",figs,"\n"))
sessionInfo()
```
